Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude

### 2016-11-04 RMS/final-version/main.tex
first final version finished

\author{
  \vskip 1em
  Jiaxiang~Liu,
  Min~Zhou,
  Xiaoyu~Song, \emph{Member}, \emph{IEEE},
  Ming~Gu,
  and Jiaguang~Sun

  \thanks{ 
    Manuscript received November 8, 2015; revised March 30,
    2016 and July 13, 2016; accepted October 20, 2016. This work was
    supported in part by NSFC Program (No.\ 91218302, No.\ 61527812,
    No.\ 91218302), National Science and Technology Major Project
    (No.\ 2016ZX01038101), MIIT IT funds (Research and application of
    TCN key technologies) of China, and The National Key Technology
    R\&D Program (No.\ 2015BAG14B01-02).

@@

It is even more crucial to ensure the reliability of an implementation
instead of the algorithm, when RMS serves in a safety-critical
system. When analyzing a realistic implementation, theoretical results
may be no more applicable. For instance, even though the conditions
derived from algorithm analysis are satisfied, schedulability can be
broken by overhead in the system, or by the interrupt mask mechanism
which may delay interrupt handling. On the other hand, correctness of
the implementation with respect to the algorithm is difficult to be
verified by the traditional methods such as testing and simulation due
to their incompleteness. Extensive effort to apply formal methods,
such as model checking and theorem proving, has been made to analyze
safety-critical systems for the past few
years~\cite{DBLP:journals/tie/MiyawakiMSYV05,DBLP:journals/iandc/MeseguerR13,DBLP:journals/cacm/Leroy09,DBLP:conf/sosp/KleinEHACDEEKNSTW09}. However,
as far as we know, few~\cite{TianD2011,DBLP:conf/iceccs/CuiDT14}
attempt to analyze the RMS algorithm, while no work for
implementations of RMS is found.

@@

\section*{Acknowledgment}
The authors would like to thank the reviewers and editors for their
invaluable comments and suggestions.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{J_Liu.jpg}}]%
{Jiaxiang Liu} received his B.S.\ degree in computer software from
Tsinghua University, China in 2010. He is now a Ph.D.\ candidate in
the Department of Computer Science and Technology, Tsinghua
University, China. His research interests include formal methods,
rewrite systems and embedded systems.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{M_Zhou.jpg}}]%
{Min Zhou} received his B.S.\ degree from the Department of
Mathematical Science and Ph.D.\ degree from the Department of Computer
Science and Technology, Tsinghua University, China in 2007 and 2014,
respectively. He is now a lecturer at the School of Software, Tsinghua
University. His research interests include model checking, program
analysis and testing.
\end{IEEEbiography}

%% \vspace{-2cm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{X_Song.jpg}}]%
{Xiaoyu Song} () received the Ph.D.\ degree from the University of
Pisa, Italy, in 1991. From 1992 to 1998, he was on the faculty at the
University of Montreal, Canada. He joined the Department of Electrical
and Computer Engineering at Portland State University in 1998, where
he is now a professor. He was an editor of IEEE Transactions on VLSI
Systems and IEEE Transactions on Circuits and Systems. He was awarded
an Intel Faculty Fellowship from 2000 to 2005. His research interests
include formal methods, design automation, embedded systems and
emerging technologies.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{M_Gu.jpg}}]%
{Ming Gu} is a professor at the School of Software, Tsinghua
University, China. She is also vice-director of Key Laboratory for
Information System Security, Ministry of Education, China. Her
research interests include software formal methods, software
trustworthiness and middleware technology.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{J_Sun.jpg}}]%
{Jiaguang Sun} is a professor and dean of the School of Information
Science and Technology in Tsinghua University, China. He is also a
member of the Chinese Academy of Engineering, director of Ministry of
Education Key Laboratory for Information System Security, and director
of Tsinghua National Laboratory for Information Science and
Technology, China. His research interests include computer graphics,
computer-aided design, formal verification of software, software
engineering, and system architecture.
\end{IEEEbiography}

>>>>

\author{
  \vskip 1em
  Jiaxiang~Liu,
  Min~Zhou,
  Xiaoyu~Song, \emph{Senior Member}, \emph{IEEE},
  Ming~Gu,
  and Jiaguang~Sun

  \thanks{ 
    Manuscript received November 8, 2015; revised March 30,
    2016 and July 13, 2016; accepted October 20, 2016. This work was
    supported in part by NSFC Program (No.\ 91218302, No.\ 61527812,
    No.\ 61402248), National Science and Technology Major Project
    (No.\ 2016ZX01038101), MIIT IT funds (Research and application of
    TCN key technologies) of China, and The National Key Technology
    R\&D Program (No.\ 2015BAG14B01-02).

@@

It is even more crucial to ensure the reliability of an implementation
instead of the algorithm, when RMS serves in a safety-critical
system. When analyzing a realistic implementation, theoretical results
may be no more applicable. For instance, even though the conditions
derived from algorithm analysis are satisfied, schedulability can be
broken by overhead in the system, or by the interrupt mask mechanism
which may delay interrupt handling. On the other hand, correctness of
the implementation with respect to the algorithm is difficult to be
verified by the traditional methods such as testing and simulation due
to their incompleteness. Extensive effort to apply formal methods,
such as model checking and theorem proving, has been made to analyze
safety-critical systems for the past few
years~\cite{DBLP:journals/tie/JiangZLDSGS15,DBLP:journals/iandc/MeseguerR13,DBLP:journals/cacm/Leroy09,DBLP:conf/sosp/KleinEHACDEEKNSTW09}. However,
as far as we know, few~\cite{TianD2011,DBLP:conf/iceccs/CuiDT14}
attempt to analyze the RMS algorithm, while no work for
implementations of RMS is found.

@@

%% \section*{Acknowledgment}
%% The authors would like to thank the reviewers and editors for their
%% invaluable comments and suggestions.

@@

\vspace{-5mm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{1.jpg}}]%
{Jiaxiang Liu} received his B.S.\ degree in software engineering from
Tsinghua University, China in 2010. He is currently working toward the
Ph.D.\ degree in computer science at Tsinghua University, China.

His research interests include formal methods, rewrite systems and
embedded systems.
\end{IEEEbiography}

\vspace{-5mm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{M_Zhou1.jpg}}]%
{Min Zhou} received his B.S.\ degree in mathematics and applied
mathematics, and the Ph.D.\ degree in computer science from Tsinghua
University, China in 2007 and 2014, respectively.

He is currently a lecturer at the School of Software, Tsinghua
University, China. His research interests include model checking,
program analysis and testing.
\end{IEEEbiography}

\vspace{-5mm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{X_Song1.jpg}}]%
{Xiaoyu Song} received the Ph.D.\ degree from the University of Pisa,
Italy, in 1991. From 1992 to 1998, he was on the faculty at the
University of Montreal, Canada. He joined the Department of Electrical
and Computer Engineering at Portland State University in 1998, where
he is now a professor. He was an editor of IEEE Transactions on VLSI
Systems and IEEE Transactions on Circuits and Systems. He was awarded
an Intel Faculty Fellowship from 2000 to 2005. His research interests
include formal methods, design automation, embedded systems and
emerging technologies.
\end{IEEEbiography}

\vspace{-5mm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{M_Gu1.jpg}}]%
{Ming Gu} received the B.S.\ degree in computer science from the
National University of Defense Technology, China in 1984, and the
M.S.\ degree in computer science from the Chinese Academy of Science,
China in 1986.

She is currently a professor at the School of Software, Tsinghua
University, China. 
%% She is also vice-director of Key Laboratory for
%% Information System Security, Ministry of Education, China. 
Her research interests include software formal methods, software
trustworthiness and middleware technology.
\end{IEEEbiography}

\vspace{-5mm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{J_Sun1.jpg}}]%
{Jiaguang Sun} received the B.S.\ degree in automation science from
Tsinghua University, China in 1970.

He is currently a professor and
dean of the School of Information Science and Technology in Tsinghua
University, China. He is also a member of the Chinese Academy of
Engineering, and director of Tsinghua National Laboratory for
Information Science and Technology, China. 
His research interests
include computer graphics, computer-aided design, formal verification
of software, software engineering and system architecture.
\end{IEEEbiography}
